\documentclass[11pt,letterpaper]{article}

%Use Palantino font
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\usepackage{microtype}

%Hyperref package... clickable doi links
\usepackage[usenames,hyperref]{xcolor}
\definecolor{mediumblue}{rgb}{0.0,0.0,0.8}
\usepackage[colorlinks=true,urlcolor=mediumblue,linkcolor=black]{hyperref}

%Finer control of margins and page geometry
\usepackage{geometry}
\geometry{paper=letterpaper,lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in}
\geometry{headheight=\baselineskip}

% %Header...
\usepackage{fancyhdr}
\usepackage{lastpage}

%Footnotes
\usepackage{footmisc}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%Use less space before and after section titles
\usepackage[]{titlesec}
\titlespacing*{\subsection}{0pt}{0.3\baselineskip}{0.\baselineskip}
\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.\baselineskip}
%Format section titles to include a horizontal bar
\titleformat{\section}{\normalfont\Large}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

%Configure spacing...
\setlength{\parindent}{0pt}                 %Don't indent paragraphs
\setlength{\parskip}{0.4\baselineskip}      %Spacing after paragraphs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Page numbering ----------------------------------
\pagestyle{empty}           %No auto page numbers
\pagestyle{fancy}
\fancyfoot{}                        %Clear foter
\fancyhead{}                        %No header
% \lfoot{\small S. T. Salesky }   %My name in header
\lfoot{\small S. T. Salesky }   %My name in header
\rfoot{\small \thepage\ of \pageref{LastPage}}   %My name in header
\renewcommand{\headrulewidth}{0pt}
%-------------------------------------------------

%Header with contact information
\begin{center}
    \textbf{\Large Scott T. Salesky} \\
    Department of Civil Engineering \\
    The University of British Columbia \\
    2002 - 6250 Applied Science Lane \\
    Vancouver, BC V6T 1Z4 Canada \\
    \begin{tabular}{c c}
        % Tel: 1-604-822-2637 & Fax: 1-604-822-6901
        Tel: 1-810-412-8580 & Fax: 1-604-822-6901
    \end{tabular} \\
    Email: \texttt{scott.salesky@ubc.ca}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Research Interests}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Civil Version
Turbulence, Atmospheric Boundary Layer, Large Eddy Simulation, Environmental Fluid \\ Mechanics,
Earth-Atmosphere Interactions, Multiphase Flows, Surface Hydrology, Evaporation 
% %Civil Version
% Environmental Fluid Mechanics, Surface Hydrology, Atmospheric Boundary Layer,
% Large Eddy Simulation, Turbulence, Evaporation, Land-Atmosphere Interactions,
% Snow and Sediment Transport, Multiphase Flows

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Education}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{l l}
2014 & \textbf{Ph.D. Meteorology} \\
% 2014 & \textbf{Ph.D. Atmospheric Science} \\
      & The Pennsylvania State University, University Park, PA \\
      & {\small \textbf{Dissertation:}} \textit{\small``Monin-Obukhov similarity and convective organization in the unstable atmospheric}\\
      & \textit{\small boundary layer''} \\%[1.5\parskip]
      & {\small \textbf{Advisor:}} {\small Marcelo Chamecki} \\[1.5\parskip]

2010 & \textbf{M.S. Meteorology} \\
% 2010 & \textbf{M.S. Atmospheric Science} \\
      & The Pennsylvania State University, University Park, PA \\
      & {\small \textbf{Thesis:}} \textit{\small ``Similarity models of subfilter-scale energy and temperature variance for large eddy simulations} \\
      & \textit{\small of the atmospheric boundary layer.''} \\%[1.5\parskip]
      & {\small \textbf{Advisor:}} {\small Marcelo Chamecki} \\[1.5\parskip]

2008 & \textbf{B.S. Science Education}, \textit{Summa Cum Laude} \\
              & Martin Luther College, New Ulm, MN
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Professional Appointments}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabular}{l l}
2014--present & \textbf{Postdoctoral Fellow}, Department of Civil Engineering \\
              & The University of British Columbia \\[1.5\parskip]
2008--2014 & \textbf{Graduate Research Assistant}, Department of Meteorology \\
                 & The Pennsylvania State University
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Honors and Awards}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{l l}
2014 & \textbf{Penn State Alumni Association Dissertation Award} \\
     & The Pennsylvania State University \\[1.5\parskip]

2014 & \textbf{John C. Wyngaard Graduate Research Award} \\
     & Department of Meteorology, The Pennsylvania State University \\[1.5\parskip]

2007 & \textbf{Barbara Klockziem Scholarship} \\
     & Martin Luther College

\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Peer-Reviewed Publications}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Li, D., \textbf{S.T. Salesky}, and T. Banerjee (2016) Connections between
the Ozmidov scale and mean velocity profile in stably stratified atmospheric
surface layers. \textit{Journal of Fluid Mechanics}, \textbf{797}, R3. [\href{http://doi.org/10.1017/jfm.2016.311}{\textsc{doi}}]

Banerjee, T., G.G. Katul, \textbf{S.T. Salesky}, and M. Chamecki (2014) Revisiting the formulations for longitudinal velocity variance in the unstable atmospheric surface layer. \textit{Quarterly Journal of the Royal Meteorological Society}, \textbf{141(690)}:1699--1711. [\href{http://doi.org/10.1002/qj.2472}{\textsc{doi}}] 

\textbf{Salesky, S.T.}, G.G. Katul, and M. Chamecki (2013) Buoyancy effects on the integral lengthscales and mean velocity profile in atmospheric surface layer flows. \textit{Physics of Fluids}, \textbf{25},105101. [\href{http://doi.org/10.1063/1.4823747}{\textsc{doi}}]

\textbf{Salesky, S.T.} and M. Chamecki (2012) Random errors in turbulence measurements in the atmospheric surface layer: implications for Monin-Obukhov similarity theory. \textit{Journal of the Atmospheric Sciences}, \textbf{69}(12):3700-3714. [\href{http://doi.org/10.1175/JAS-D-12-096.1}{\textsc{doi}}]
%, doi:10.1175/JAS-D-12-096.1 

\textbf{Salesky, S.T.} and M. Chamecki  (2012) A similarity model of subfilter-scale energy for large eddy simulations of the atmospheric boundary layer. \textit{Boundary-Layer Meteorology}, \textbf{145}(1):69-91. [\href{http://doi.org/10.1007/s10546-011-9618-0}{\textsc{doi}}]
%, doi:10.1007/s10546-011-9618-0 

\textbf{Salesky, S.T.}, M. Chamecki, and N.L.Dias (2012) Estimating the random error in eddy-covariance based fluxes and other turbulence statistics: the filtering method. \textit{Boundary-Layer Meteorology}, \textbf{144}(1):113-135. [\href{http://doi.org/10.1007/s10546-012-9710-0}{\textsc{doi}}]
%, doi:10.1007/s105-012-9710-0 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Accepted Manuscripts} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Submitted Manuscripts}\footnote[2]{Submitted manuscripts available upon request (\texttt{scott.salesky@ubc.ca}).}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Salesky, S.T.}, M. G. Giometto, M. Chamecki, M. Lehning, and M.B. Parlange (2016) 
The transport and deposition of heavy particles in complex terrain: insights from an Eulerian model
for large eddy simulation. Submitted to \textit{Water Resources Research}.

Ghannam, K., T. Duman, \textbf{S.T. Salesky}, M. Chamecki, and G. G. Katul (2016)
The nonlocal character of turbulence asymmetry in the convective atmospheric boundary
layer. Submitted to \textit{Quarterly Journal of the Royal Meteorological Society}.

\textbf{Salesky, S.T.}, M. Chamecki, and E. Bou-Zeid (2016) On the nature of the transition
between roll and cellular organization in the convective boundary layer. Submitted to
\textit{Boundary-Layer Meteorology}.

Chamecki, M., N.L. Dias, and \textbf{S.T. Salesky} (2016) Scaling laws for 
the structure function in the atmospheric surface layer. Submitted to 
     \textit{Physics of Fluids}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Manuscripts in Preparation}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Salesky, S.T.}, M. Giometto, M. Lehning, and M.B. Parlange (2016)
The preferential erosion and deposition of heavy particles over erodible beds.

\textbf{Salesky, S.T.}, M. Giometto, A. Christen, and M.B. Parlange (2016)
Scalar dispersion from point and area sources in realistic urban environments.

% \textbf{Salesky, S.T.}, M. Giometto, M. Chamecki, M. Lehning, and M.B. Parlange (2016) 
% The transport and deposition of heavy particles in complex terrain: insights from an Eulerian model
% for large eddy simulation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Invited Talks}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Salesky, S.T.}, 2016. Coherent structures and turbulent transport in the atmospheric boundary layer: Insights 
from large eddy simulation. Department of Biological and Ecological Engineering Seminar. Oregon State University. 
April 29, 2016.

\textbf{Salesky, S.T.}, 2014. Turbulent transport and convective organization in the unstable atmospheric boundary layer. Fluids Laboratory Seminar. University of British Columbia. April 9, 2014. 

\textbf{Salesky, S.T.}, and M. Chamecki, 2011. Deviations from Monin-Obukhov similarity. Department of Meteorology `Frank' Talk. The Pennsylvania State University, October 28, 2011. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Conference Presentations}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \textbf{S.T. Salesky}, M.G. Giometto, A. Christen, and M.B. Parlange, 2016.
% Scalar dispersion from point sources and area in realistic urban
% environments.  AMS General Meeting.

% \textbf{S.T. Salesky}, M.G. Giometto, A. Christen, and M.B. Parlange, 2016. 
% Scalar dispersion from point sources in realistic urban environments. 
% AGU Fall Meeting.

% \textbf{Parlange, M.B.}, M.G. Giometto, P. Egli, M.F. Schmidt, R.T. Tooke, 
% N.C. Coops, \textbf{S.T. Salesky}, and A. Christen, 2016. 
% Effects of urban trees on mean wind, turbulence and momentum exchance
% within and above a realistic urban canopy. AGU Fall Meeting.

% \textbf{Salesky, S.T.}, M.G. Giometto, M. Lehning, and M.B. Parlange, 2016.
% The preferential erosion and deposition of heavy particles over erodible beds.
% 69th Annual Meeting, APS/DFD. Portland, OR, November 24-26, 2016. 

\textbf{Salesky, S.T.}, M. Chamecki, and E. Bou-Zeid, 2016. On the nature of the
transition from roll to cellular organization in the convective boundary layer.
22nd Symposium on Boundary Layers and Turbulence. Salt Lake City, UT, June
20-24, 2016.

Parlange, M.B., \textbf{S.T. Salesky}, M.G. Giometto, M. Chamecki, and M.
Lehning, 2016.  The preferential deposition of snow in complex terrain: an LES
investigation.  22nd Symposium on Boundary Layers and Turbulence. Salt Lake
City, UT, June 20-24, 2016.

Chamecki, M., Y. Pan, N.L. Dias, and \textbf{S.T. Salesky}, 2016. Scaling laws for
structure functions in the lowest layers of the ABL.  22nd Symposium on
Boundary Layers and Turbulence. Salt Lake City, UT, June 20-24, 2016.

Giometto, M.G., E. Trujillo, K.C. Leonard, T.L. Maksym, F. Comola, \textbf{S.T.
  Salesky}, C. Meneveau, M. Lehning, and M.B. Parlange, 2016.  LES modeling of
wind over Antarctic snow-ice formations using a dynamic surface roughness
approach.  22nd Symposium on Boundary Layers and Turbulence. Salt Lake City,
UT, June 20-24, 2016.

Ghannam, K., G.G. Katul, \textbf{S.T. Salesky}, and M. Chamecki, 2015. Closure
of the heat flux budget with the ejection-sweep cycle in the convective
boundary layer. Fall Meeting, AGU. San Francisco, CA, December 14-18, 2015.

\textbf{Salesky, S.T.}, M. Giometto, M. Chamecki, M. Lehning, and M.B.
Parlange, 2015. The preferential deposition of snow in complex terrain: An LES
investigation. Fall Meeting, AGU. San Francisco, CA, December 14-18, 2015.

\textbf{Salesky, S.T.}, M. Giometto, M. Chamecki, and M.B. Parlange, 2015.
Blowing snow in complex terrain - an LES investigation. International
Conference on Model Integration Across Disparate Scales in Complex Turbulent
Flow Simulation. State College, PA, June 15--17, 2015. 

Banerjee, T., G.G. Katul, \textbf{S.T. Salesky}, and M. Chamecki, 2014.
Logarithmic scaling in the longitudinal velocity variance explained by a
spectral budget in a neutral and unstable atmosphere. APS March Meeting,
Denver, CO, March 3-7, 2014. 

\textbf{Salesky, S.T.}, G.G. Katul, and M. Chamecki, 2013. Buoyancy effects on
the mean velocity profile in atmospheric surface layer flows. 66th Annual
Meeting, APS/DFD. Pittsburgh, PA, November 24-26, 2013. 

\textbf{Salesky, S.T.} and M. Chamecki, 2012. Scatter in plots of Monin-Obukhov
similarity functions: random errors or missing physics? American Meteorological
Society 20th Symposium on Boundary Layers and Turbulence. Boston, MA, July
8-13, 2012. 

Chamecki, M. and \textbf{S.T. Salesky}, 2012. A new approach to estimate random
errors in turbulence statistics. American Meteorological Society 20th Symposium
on Boundary Layers and Turbulence. Boston, MA, July 8-13, 2012. 

Chamecki, M., and \textbf{S.T. Salesky}, 2011. Spatial locality of turbulent
fluxes: toward local flux-gradient relationships in the atmospheric surface
layer. Fall Meeting, AGU. San Francisco, CA, December 5-9, 2011. 

\textbf{Salesky, S.T.}, and M. Chamecki, 2011. Spatial locality of turbulent
fluxes: the filtering approach. 64th Annual Meeting, APS/DFD. Baltimore, MD,
November 20, 2011. 

\textbf{Salesky, S.T}. and M. Chamecki, 2011: A similarity model of
subfilter-scale scalar variance for large eddy simulations of the atmospheric
boundary layer. 14th Annual Environmental Chemistry Student Symposium. The
Pennsylvania State University, April 9, 2011. 

\textbf{Salesky, S.T.} and M. Chamecki, 2010: A local model of the
subfilter-scale energy for LES of the atmospheric boundary layer. 19th
Symposium on Boundary Layers and Turbulence, Keystone, CO, August 6, 2010. 

\textbf{Salesky, S.T.} and M. Chamecki, 2010: A similarity model of the
subfilter-scale energy for LES of the ABL. John C. Wyngaard Symposium, The
Pennsylvania State University, June 25, 2010. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Teaching Experience}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{The Pennsylvania State University}

\begin{tabular}{l l}
Spring, 2014 & Substitute Lecturer, \textit{Atmospheric Dynamics} (6 lectures) \\
Spring, 2013 & Teaching Assistant, \textit{Application of Computers to Meteorology} \\
Fall, 2008 & Teaching Assistant, \textit{Introductory Meteorology} \\
\end{tabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Professional Memberships}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Since 2014: American Geophysical Union \\
% Since 2010: American Physical Society \\
% Since 2009: Chi Epsilon Pi \\
% Since 2006: American Meteorological Society 

American Geophysical Union \\
American Physical Society \\
American Meteorological Society 

% Chi Epsilon Pi \\
% Penn State Alumni Association

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Other Professional Activities}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Reviewer of manuscripts for \textit{Advances in Water Resources},
\textit{Agricultural and Forest Meteorology},
\textit{Atmosphere},
\textit{Atmospheric Measurement Techniques},
\textit{Atmospheric Science Letters}, \textit{Boundary-Layer Meteorology},
\textit{Environmental Fluid Mechanics}, \textit{Journal of the Atmospheric
  Sciences}, \textit{Journal of Geophysical Research}, \textit{Weather and Forecasting} 

Session chair, 22nd Symposium on Boundary Layers and Turbulence (June 2016).

Invited attendee to The Burgers Program 2010 Research School in Fluid Dynamics, Topics in Turbulence (May 2010). 
Center for Scientific Computation and Mathematical Modeling, University of Maryland, College Park, MD 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\textsc{Personal}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
United States citizen

%Footer with date last updated
\bigskip
{\small Last updated: \today}

\end{document}
